\documentclass{article}
\author{Alex Hiller - 11850637}
\title{Power Circuit Theory - Lab Report 3}

% Type-setting
\setlength{\parindent}{0cm}
\setlength{\parskip}{0.125cm}
\pagenumbering{gobble}
\usepackage[margin=2cm]{geometry} % Formatting
\usepackage{titlesec}
% titleformat{\command}[shape]{format}{label}{separation of label to body}{Before code}[After code]
\titleformat{\section}{\huge \bfseries}{}{0em}{\clearpage}[]
\titleformat{\subsection}{\Large \bfseries}{}{0em}{}[]
\titleformat{\subsubsection}{\bfseries}{}{0em}{}[]

% Packages
\usepackage{amsmath}              % Mathematics
\usepackage{amssymb}              % Mathematics
\usepackage{listings}             % Listings
\usepackage{color}                % Listings
\usepackage{courier}              % Listings
\usepackage[american]{circuitikz} % Circuits

% Custom Commands
\newcommand{\vc}[2]{\mathbf{#1}_{#2}}

% Listing Pre-Requisites
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
  backgroundcolor=\color{backcolour},   
  commentstyle=\color{codegreen},
  keywordstyle=\color{magenta},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\footnotesize,
  breakatwhitespace=false,         
  breaklines=true,                 
  captionpos=b,                    
  keepspaces=true,                 
  numbers=left,                    
  numbersep=5pt,                  
  showspaces=false,                
  showstringspaces=false,
  showtabs=false,                  
  tabsize=2
}
\lstset{style=mystyle} 


\begin{document}
\maketitle

%\listoffigures

\clearpage

\section{Y-Neutral/Y-Neutral Transformer}

\subsection{DC Resistance of the Windings}

The wiring used for measuring the DC resistance of the transformer is as below. Resistance was measured for all three phases simultaneously.

\begin{centering}

\begin{circuitikz} 
  \draw (1,0) to[voltmeter] (1,3);
  \draw (3.2,0) to[V=$V'$] (3.2,3);
  \draw (1,3) to (3.2,3);
  \draw (1,0) to (3.2,0);
  \draw (3.2,3) to[ammeter] (4.7, 3);
  \draw (4.7,3) to[L=Phase A ] (6.7,3);
  \draw (6.7,3) to[L=Phase B] (8.7,3);
  \draw (8.7,3) to[L=Phase C] (10.7,3);
  \draw (10.7,3) to (10.7,0);
  \draw (10.7,0) to (1,0);
\end{circuitikz}

\end{centering}



\subsection{Explain the reasons for your position of the ammeter and the voltmeter}
The voltmeter comes after the resistor bank so that we both limit the current to safe levels as well as measure the primary voltage.

The ammeter is placed before the branching of the conductor into each phase of the transformer. This gives us $3 I_0$ or 3 times the current in each phase of the transformer. Measuring when the current is larger allows the error of the instrument to be reduced in comparison to one phase was being measured.


\begin{equation}
  V_1 = 0.6
\end{equation}

\begin{equation}
  I_1 = V_2 = 0.28
\end{equation}

\begin{equation}
  I_2 = 1.016
\end{equation}

\begin{equation}
  R_1 = 0.48
\end{equation}

\begin{equation}
  R_2 = 0.27
\end{equation}

\subsection{Measured Voltage and Current on the Primary Side of the Transformer}

Primary Voltage:
\begin{equation}
  | V^{'} | = 4.53 \text{V}
\end{equation} 

\begin{equation}
  | I^{'} | = 5.7 \text{A}
\end{equation} 

\subsection{Calculate the Transformer's Parameters} 

\begin{equation}
  Z_b = \frac{ \left( V_{base} \right)^2  }{S_{base}} = \frac{\left( \sqrt{3} \times 240 \right)^2}{4500} = 38.400 \Omega
\end{equation}

\begin{equation}
  R_0 = \frac{4.53}{5.70} \ \frac{1}{38.4} = 0.02070 \ (p.u.)
\end{equation}

\begin{equation}
  |Z_0 | = \frac{| V_0 |}{| I_0 |} = \frac{| V^{'} |}{| \frac{I^{'}}{3} |} = \frac{2.3842}{Z_b} = 0.0621 \ (p.u.)
\end{equation}

\begin{equation}
  X_{0} = \sqrt{| Z_0 |^{2} - R^2_0} = 0.05855  \ (p.u.)
\end{equation}

\subsection{Measure the secondary neutral current with the Fluke clamp meter} 

\begin{equation}
  | I^{''} | = 10.02 \ A \ \text{(rms)}
\end{equation}

\subsection{Measure the voltage between the neutral points with DMM} 
\begin{equation}
  | V_{Nn} | = 3.9 \text{V}
\end{equation}

This measurement was oscillating a lot.

\subsection{Draw the zero sequence equivalent circuit of the transformer}
\begin{centering}

\begin{circuitikz} \draw
  (0,3) to[R=$R_0$] (3,3)
  (3,3) to[L=$X_0$] (6,3);
\end{circuitikz}

\begin{circuitikz} \draw
  (0,0) -- (6,0); 
\end{circuitikz}

\end{centering}

\subsubsection{Explain:} 
The impedance of the transformer directly impedes the current on the secondary side.

\section{Y-Neutral to Y Transformer} 

If $|I'|$ = 5.4 A, then

\subsection{Predict $|I_s|$}

\begin{equation}
  |I_s | = \frac{N_p}{N_s} | I_p | = \frac{2}{1} (5.4) = 10.8 \text{ A}
\end{equation}

\subsubsection{Explain:} 
Current through an ideal transformer is related through the turns ratio as seen in the equation above.

\subsection{If $|I^{'} | = $ 5.4A, expectations are that:}

$V^{'}$ to be: Larger

$Z_0$ to be: Magnetising 

The current in each primary winding to be: The same.

\subsubsection{Give explanations using Faraday's Law, Ampere's Law and the magnetic equivalent circuit} 

(?)


\subsection{Measure voltage, current and power one the primary side of the transformer} 

Primary Voltage:
\begin{equation}
  | V^{'} | = 16.95 \text{ V (rms)}
\end{equation}

Primary Current:
\begin{equation}
  | I^{'} | = \frac{5.53}{3} = 1.843 \text{ A (rms)}
\end{equation}

Primary Power:
\begin{equation}
  P^{'} = 21 \text{ W}
\end{equation}

Secondary Winding Current:
\begin{equation}
  | I_{s} | = 0.4 \text{ A (rms)}
\end{equation}

\subsection{Calculate the transformer's parameters (referred to the primary)} 

\begin{equation}
  \frac{1}{3} R_0 = \frac{P^{'}}{|I^{'} |^{2}} = 6.186 \text{ $\Omega$ } \Rightarrow 0.161  \text{ (p.u.)}
\end{equation}

\begin{equation}
  R_0  = 0.161 \times 3 = 0.483 \text{ (p.u.)}
\end{equation}

Comparing $R_0$ with that measured in part 1: Much higher. 

\begin{equation}
  | Z_0 | = \frac{| V_0 |}{| I_0 |} = \frac{| V' |}{| \frac{I^{'}}{3}|} = 27.591 \Rightarrow 0.71851 \text{ (p.u.)}
\end{equation}

\begin{equation}
  X_0 = \sqrt{| Z_0 |^{2} - R^{2}_0} = 0.53195 \text{ (p.u.)}
\end{equation}

\subsection{Draw the zero sequence equivalent circuit of the transformer} 

\begin{centering}

\begin{circuitikz} \draw
  (0,0) to[R=$$] (2,0) --
  (2,0) to[L=$$] (4,0)
  (0,-1) to (7, -1)
  (5,0) to (7,0)
  (,);
\end{circuitikz}

\end{centering}

\subsubsection{Explain} 
This is as per the lecture slides. 

\subsection{Clamp meter measurements of each primary winding} 

\begin{equation}
  | I^{'}_{A} | = 1.70 \text{ A}
\end{equation}

\begin{equation}
  | I^{'}_{B} | = 1.74 \text{ A}
\end{equation}

\begin{equation}
  | I^{'}_{C} | = 1.59 \text{ A}
\end{equation}

\subsubsection{The measurements are slightly unequal, this could be because of any of the following:} 

\begin{itemize}
  \item Imbalance of heat amongst the inductors in each phase.
  \item Differences in absolute impedance, independent of temperature.
  \item Faulty measurement equipment.
  \item Tolerances in the measurement equipment.
  \item Experimental error.
\end{itemize}

\subsection{With secondary terminals open-circuited and $|I^{'}| = 5.4$ A} 

\subsubsection{Primary voltage measured was:}
\begin{equation}
  | V^{'} | = 16.94 \text{ V (rms)}
\end{equation}

\subsubsection{Calculated zero sequence impedance is:} 

\begin{equation}
  | Z_0 | = \frac{16.94}{5.4} \frac{1}{Z_b} = 0.081694  \text{ (p.u.)}
\end{equation}

\subsection{Draw the zero sequence equivalent circuit of the transformer} 

\begin{centering}

\begin{circuitikz} \draw
  (0,0) to[R=$$] (2,0) --
  (2,0) to[L=$$] (4,0)
  (0,-1) to (7, -1)
  (5,0) to (7,0)
  (5,0) to (5,-1);
\end{circuitikz}

\end{centering}

\subsubsection{Explain} 

From the primary side the impedance is infinite. On the secondary side the current is high and resistance is theoretically zero.

\subsection{Comparing the calculated transformer's parameters with the zero sequence impedance} 
These impedances must be the leakage impedance? Seems too small for a magnetising impedance.

\section{Y-Neutral to Delta Transformer} 

\subsection{Measured Voltage, Current and Resistance on Primary Side} 

\begin{equation}
  | V ^{'} | = 3.036 \text{ V}
\end{equation}

\begin{equation}
  | I ^{'} | = 1.8 \text{ A}
\end{equation}

Per-phase DC resistance:
\begin{equation}
  R_0 = \frac{1.687}{38.4} = 0.04392 (p.u.)
\end{equation}

\subsection{DMM measurement of the phase voltages to primary neutral on the secondary side} 

\begin{equation}
  | V ^{''} _{a} | = 0.1 \text{ V}
\end{equation}

\begin{equation}
  | V ^{''} _{b} | = 0.1 \text{ V}
\end{equation}

\begin{equation}
  | V ^{''} _{c} | = 0.1 \text{ V}
\end{equation}

\subsection{Measured secondary current} 

\begin{equation}
  | I _{d} | = 3.34 \text{ A (rms)} 
\end{equation}

\subsection{Transformer's calculated parameters (referred to the primary)} 

\begin{equation}
  Z _0 = R _0 + j X _0 = 0.04392 + j0.124 \ (p.u.) 
\end{equation}

\subsection{Zero-sequence equivalent of the transformer} 

\begin{centering}

\begin{circuitikz} \draw
  (0,0) to[R=$R_0$] (2,0) 
  to[L=$X_0$, -] (4,0) to (4,-1)
  (0,-1) -- (6,-1)
  (5,0) -- (6,0);
\end{circuitikz}

\end{centering}

\subsubsection{Explain:} 

The impedance can only be seen from the primary side.

\subsection{If a secondary line terminal was shorted to the "earth" (primary neutral), what would be the resulting current?} 

Negative of the primary current.

\subsection{Is $Z _0$ a leakage or magnetising impedance?} 

Magnetising.

\subsection{Is the delta secondary a short-circuit to zero sequence currents?} 

No.

\subsection{Comparison of the $Z _0$ for the three confgurations} 

The $Z_0$ of the configurations without a grounding on the secondary side are much higher. 

\section{Positive \& Negative Sequence Impedance} 

Primary Voltage:
\begin{equation}
  | V _{sc} | = 7.89 \text{ V (rms)}
\end{equation}

Primary Current:
\begin{equation}
  | I _{sc} | = 5.4 \text{ A (rms)}
\end{equation}

Primary Power:
\begin{equation}
  P _{sc} = 31 \text{ W}
\end{equation}

\subsection{Transformer's Calculated Parameters} 

\begin{equation}
  R_1 = \frac{P_{sc}}{| I _{sc}|^2} = 1.0631 \ \Omega \ \Rightarrow \ 0.027685 \ (p.u.)
\end{equation}

Comparing this with that found in Part 1:


\begin{equation}
  | Z _1 | = | Z _2 | = \frac{|V_{sc}|}{|I_{sc}|} = 1.4611 \ \Omega \ \Rightarrow \ 0.03805 \ (p.u.)
\end{equation}

\begin{equation}
  X_1 = \sqrt{| Z _1 |^2 - R^2 _1} = 0.026103 \ (p.u.)
\end{equation}

\subsection{Comparing $R1$ and $R0$} 



\subsubsection{Explain} 

Both of these resistances are measured from the primary side and are hence going to be related to one another.

\subsection{Positive \& negative sequence test circuit for magnetising $Z$ } 

\subsubsection{Why such a circuit is used:} 

Because it doesn't matter which side the positive sequence enters the transformer if we're attempting to determine these impedances.

\subsubsection{Determining $R _{1m}$ $X _{1m}$ and  $Z _{1m}$}

Using the voltage and current measurements, you can determine $R_{lm}$ and $X_{lm} \ \Rightarrow \ Z_{lm} = R_{lm} + j X_{lm}$

\subsection{Determining $Z_{0m}$} 

<++>

\subsubsection{Equivalent Circuits} 

<++>

\subsubsection{Relevant Equations} 

<++>

\subsubsection{Experimental setup and equipment} 

<++>

\end{document}
